
\cvsection{Publications}

\begin{addtab}
\cvsubsection{Journal Papers}
\end{addtab}

\begin{tabitemize}
\item \textbf{Bing Tan}, Zheng Zhou, {Xiaolong Qin}*. Accelerated projection-based forward-backward splitting algorithms for monotone inclusion problems. \textit{J. Appl. Anal. Comput.} 2020, in press. (\physlablink{https://www.physlab.org/experiment/newtons-cradle/}).

\item {{Zheng Zhou}*, \textbf{Bing Tan}, Songxiao Li. An inertial shrinking projection algorithm for split common fixed point problems. \textit{J. Appl. Anal. Comput.} 2020, in press.}

\item{\textbf{Bing Tan}, Shanshan Xu, {Songxiao Li}*. Modified inertial hybrid and shrinking projection algorithms for solving fixed point problems. \textit{Mathematics} 2020, 8(2), 236.  }

\item {Yinglin Luo, {Meijuan Shang}*, \textbf{Bing Tan}. A general inertial viscosity type method for nonexpansive mappings and its applications in signal processing. \textit{Mathematics} 2020, 8(2), 288.}

\item {\textbf{Bing Tan}, Shanshan Xu, {Songxiao Li}*. Inertial shrinking projection algorithms for solving hierarchical variational inequality problems. \textit{J. Nonlinear Convex Anal.} 2020, in press.}

\item {Yinglin Luo, \textbf{Bing Tan}*, A self-adaptive inertial extragradient algorithm for solving pseudo-monotone variational inequality in Hilbert spaces. \textit{J. Nonlinear Convex Anal.} 2020, in press.}

\item {{Liya Liu}*, \textbf{Bing Tan}, {Sun Young Cho}*. On the resolution of variational inequality problems with a double-hierarchical structure. \textit{J. Nonlinear Convex Anal.} 2020, 21(2): 377--386.}
\end{tabitemize}

\begin{addtab}
	\cvsubsection{E-Preprints}
\end{addtab}

\begin{tabitemize}
\item {Jingjing Fan, {Xiaolong Qin}*, \textbf{Bing Tan}. Convergence of an inertial shadow Douglas-Rachford splitting for monotone inclusions. Submitted to \textit{Numerical Functional Analysis and Optimization}.}

\item {\textbf{Bing Tan}, Songxiao Li, {Xiaolong Qin}*. Strong convergence of inertial Mann algorithms for solving hierarchical fixed point problems. Submitted to \textit{Applicable Analysis}.}

\end{tabitemize}




%% If the NEXT page doesn't start with a \cvsection but you'd
%% still like to add a sidebar, then use this command on THIS
%% page to add it. The optional argument lets you pull up the
%% sidebar a bit so that it looks aligned with the top of the
%% main column.
% \addnextpagesidebar[-1ex]{page3sidebar}
%\clearpage

%\begin{comment}